---
title: Presentation Demo Title That Probably Wraps
subtitle: This is sort of cool subtitle, but it is rather long
author: Dr. Clifton Franklund
job: General Education Coordinator
date: Spring 2017
output:
  revealjs::revealjs_presentation:
    theme: moon
    highlight: pygments
    center: false
    transition: fade
    reveal_options:
      navigation: false
      progress: false
      slideNumber: false
      controls: false
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
```

## R Markdown
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets
<div id="left">
1. This is the first bullet
1. This is another bullet
1. Let's add another, just for fun
</div>
<div id="right">
- More can be added here
- And more after that
- I'm tired of this now
</div>

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

