---
title: Assessing General Education Program Outcomes
subtitle:  Systematic Use of Course-Level Student Data
author: Dr. Clifton Franklund
job: General Education Coordinator
date: Spring 2017
output:
  revealjs::revealjs_presentation:
    theme: moon
    highlight: pygments
    center: false
    transition: fade
    reveal_options:
      navigation: false
      progress: false
      slideNumber: false
      controls: false
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
```

## About Ferris State University
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Revised General Education

## What is assessment anyhow?

## Focusing the discussion

## Sustainable assessment
<br  /> 
<div style="font-size: 1.5em; font-weight: 800;">
>- Simplify  
>- Standardize  
>- Automate  

</div>

## Reproducible assessment

## Competencies and FLOs

## Standardizing Measures

## Standardizing Pedagogy

## Setting up TracDat

## Registering Courses

## Sending Assignments

## Standardized Data Collection

## Aggregating Student Data

## Automating Reporting

## Promoting Assessment

## Disqus

## Open Science Framework

## GitHub

## Slide with Bullets
<div id="left">
1. This is the first bullet
1. This is another bullet
1. Let's add another, just for fun
</div>
<div id="right">
- More can be added here
- And more after that
- I'm tired of this now
</div>

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

